% $Id$

\section{Accessing Documents in the Archive}

There are two principle methods for accessing documents in the archive, \emph{browsing}, and \emph{searching}. These are described below.

There are other ways in which a document may be reached:

\begin{itemize}
\item Via a URL supplied by a third party
\item Via an open archives service (e.g.\ a distributed search or citation link.)
\item Via a search engine, such as \emph{Google} or \emph{Alta Vista}.
\end{itemize}

When you reach a document in the archive, normally you'll be presented with a page called the \emph{abstract page}. This page will display some information about the document, usually including an abstract an full reference, and will show you in what full text format(s) the document is available for download.


\subsection{Browsing}

Browsing is a good way of accessing documents if you don't have a specific idea of what you're looking for. You can browse through a catalogue of subject areas, and when you reach a subject you're interested in, you can select documents that interest you from the list you're presented with.

To access the subject browse display, either select \emph{Browse by Subject} from the front page of the archive, or by selecting \emph{Browse} on the left-hand navigation bar elsewhere on the site.

You'll start with an overview of the subjects covered by the system. Next to most subjects is a number in brackets; this is the number of documents held in the archive pertaining to that subject. Select a subject that interests you, and the display will updated. If you selected a subject with documents in the archive, those documents will be listed on the display. Also some of the subject catalogue will be displayed at the top of the page, and you can click on these to move to other subject areas. To access a paper, simply click on its reference in the display.

On the abstract page, you should be able to see what subjects are pertinent to the current document. Clicking on one of those subjects will take you back to the relevant \emph{browse by subject} view.


\subsection{Searching}

The archive offers two levels of searching, \emph{simple} and \emph{advanced}. They are both similar, but the advanced form lets you perform a finer-grained search using more fields. Access the simple search using the \emph{Search the Archive} link on the front page, or using the \emph{Search} option on the left-hand navigation bar elsewhere in the archive. To perform an advanced search, use the \emph{advanced search} link at the top of the simple search page.

