\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{tabularx}

% $Id$

\title{Eprints Archive Software System Documentation}
\author{Robert Tansley \and Christopher Gutteridge}

\newcommand{\eprints}{\emph{Eprints}}


\begin{document}

\maketitle

\tableofcontents

\section{Introduction}

This document describes the workings of the Eprints archive software, and how it interacts with the other components to provide services.

What this document does not contain is an API specification. Nor does it contain detailed information about what each file in the distribution does. The code is richly commented; this information is by and large not duplicated in this document. Producing such a document would have delayed the \eprints\ release by weeks. The best way to learn about the system, and how to achieve something, is to look at the code, read the comments therein, and follow the code's example. The comprehensiveness of this document should improve over time.

Before I delve in, a short note about programming style. The code is designed to be viewed with a tab width of 3. Tabs are \emph{always} used for indentation. Indentation of eight spaces is far too much, and using a combination of spaces and tabs just causes problems.

In your site specific code, and especially if you're developing the core code itself, please follow the style of the existing code, and comment richly, to enable the \eprints\ software to be easily maintainable in the future.

\subsection{Further Help and Bug Reports}

Technical queries (\emph{not} bug reports) concerning the \eprints\ software should be sent to:

\begin{verbatim}
support@eprints.org
\end{verbatim}

General information queries should be sent to:

\begin{verbatim}
info@eprints.org
\end{verbatim}

If you suspect you have found a bug, or an error in the documentation, please check the bug reporting system at:

\begin{verbatim}
http://bugs.eprints.org/
\end{verbatim}

If the problem has not already been reported, submit a bug report to the system.

Suggestions for new features to add to the software (wishlist items) can also be submitted to the bug report system.


\input{system-body}

\end{document}
